Data Pre-Processing/Cleaning Script

### 2023-02-23 code/processing_code/processingfile_v1.qmd
part 2 of project

analysis_data_fin %>%
  mutate(Pathogen_Type = case_when(
    grepl(paste(Pathogen_Bacteria, 
                collapse = "|"), Etiology) ~ "Bacteria",
    grepl(paste(Pathogen_Parasite, 
                collapse = "|"), Etiology) ~ "Parasite",
    grepl(paste(Pathogen_Virus, 
                collapse = "|"), Etiology) ~ "Virus",
    grepl(paste(Pathogen_Poison, 
                collapse = "|"), Etiology) ~ "Poison")) %>%
  mutate(Etiology = case_when(
    Pathogen_Type == "Bacteria" ~

>>>>

analysis_data_fin %>%
  mutate(Pathogen_Type = case_when(
    grepl(paste(Pathogen_Bacteria, 
                collapse = "|"), Etiology) ~ "Bacteria",
    grepl(paste(Pathogen_Parasite, 
                collapse = "|"), Etiology) ~ "Parasite",
    grepl(paste(Pathogen_Virus, 
                collapse = "|"), Etiology) ~ "Virus",
    grepl(paste(Pathogen_Poison, 
                collapse = "|"), Etiology) ~ "Poison")) %>%
  mutate(Etiology = case_when(
    Pathogen_Type == "Bacteria" ~ which(Etiology %in% )
